\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex

\begin{wraptable}[7]{r}{40mm}
	\vspace{-8mm}
	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}
	\label{tab:benchmark}
	\vspace{-5mm}
\end{wraptable}

@@

J-ReCoVer successfully handled $115$ cases ($97.5~\%$) out of the considered
ones. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
$72~\%$ of the execution time was spent in compiling Java source code to
bytecode, which is the input of the Soot tool. Further, $27~\%$ of the execution
time was spent in the Preprocessor, in which Soot is used to transform Java
bytecode to Jimple and perform the program transformations. The time spent in
Solver is quite limited ($<1~\%$) since the real-world integer reducer programs
are usually not that big.

There is no other tool that could handle the reducers as they are. Perhaps some
other tools could be applied on the transformed programs, but the
transformations would still be needed, and our SMT-based back-end verifier (the
Solver) turned out to work efficiently. Hence, we did not feel a need to replace
it by another verification tool. Of course, in the future, this can be done if
need be.

J-ReCoVer failed in three cases out of the considered ones because the three
reducers use more complicated control structures than what J-ReCoVer currently
supports. Namely, they use a branch statement before entering the loop, i.e.,
they have the form of
$\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such
a program can be handled by more sophisticated program transformations. For
example, we can merge the two loops and push the outer branch condition into the
merged loop. Extensions of J-ReCoVer to be able to handle such constructions,
together with a support for more data types, belong among our future works.

>>>>

\begin{wraptable}[7]{r}{40mm}
	\vspace{-8mm}
	\caption{Size of the reducers.}
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Line & Variable & Branch\\
		\hline
		Min. & 5 & 4 & 0\\
		Avg. & 20.5 & 14.7 & 1.2\\
		Max. & 58 & 37 & 5\\
		\hline
	\end{tabular}

	\label{tab:benchmark}
	\vspace{-5mm}

\end{wraptable}

@@

J-ReCoVer successfully handled $115$ cases ($97.5~\%$) out of the considered
ones. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
$72~\%$ of the execution time was spent in compiling Java source code to
bytecode, which is the input of the Soot tool. Further, $27~\%$ of the execution
time was spent in the Preprocessor, in which Soot is used to transform Java
bytecode to Jimple and perform the program transformation. The time spent in
Solver is quite limited ($<1~\%$) since the real-world integer reducer programs
are usually not that big.

There is no other tool that could handle the reducers as they are. Perhaps some
other tools could be applied on the transformed programs, but the
transformation would still be needed, and our SMT-based back-end verifier (the
Solver) turned out to work efficiently. Hence, we did not feel a need to replace
it by another verification tool. Of course, in the future, this can be done if
need be.

J-ReCoVer failed in three cases out of the considered ones because the three
reducers use more complicated control structures than what J-ReCoVer currently
supports. Namely, they use a branch statement before entering the loop, i.e.,
they have the form of
$\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such
a program can be handled by more sophisticated program transformation. For
example, we can merge the two loops and push the outer branch condition into the
merged loop. Extensions of J-ReCoVer to be able to handle such constructions,
together with a support for more data types, belong among our future works.
